The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-06 paper.tex
update

  Although the high-energy CRe ($10$ --- $100$ GeV) plays a crucial role in reproducing the $\gamma$-ray map\
  within the range of $1$ --- $100$ GeV, we assume the pressure of CRe is much less than that of gas\
  throughout the simulation so that we , and the \textit{Fermi} bubbles can be outlined against the eROSITA bubbles.

@@

  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time 1.2 Myr,\
  allowing the total ejected energy $1.2\times10^{56}$ erg is between\
  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

@@

 \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp} shows\
 the pressure (top), temperature (middile), number density (bottom) of slices on $x=0$ plane\
 passing through a bipolar jet sources injecting along $z=-y$ direction from\
 the origin for a duration of 1.2 Myr under four different cases from left to right.\
 Comparison between the cases with a clumpy (first column from left)\
 and with a smooth disc (second) in a stratified atmosphere\
 shows that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
 in an uniform atmosphere (third) is spherical-shape,\
 suggesting the stratification facilitates the outer bubbles elongation significantly.\
 Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
 can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
 indicating the dense disc is crucial for\
 the axis-symmetrical outer bubbles and of the most inner bubbles formation.

\label{Results}
  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             passing through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disc (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
             indicating the dense disc is crucial for\
             the axis-symmetrical outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

  \subsection{X-ray}
  The X-ray emissivity in an energy range 0.6 --- 1.0 keV is calculated\
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\

@@

  Indeed, we find that the simulated gamma-ray\
  spectra for all latitudes exhibit a spectral cutoff at\
  similar energies 400---500 GeV, consistent with\
  the observed cutoff energy.

>>>>

  Although the high-energy CRe ($10$ -- $100$ GeV) plays a crucial role in reproducing the $\gamma$-ray map\
  within the range of $1$ -- $100$ GeV, we assume the pressure of CRe is much less than that of gas\
  throughout the simulation so that we , and the \textit{Fermi} bubbles can be outlined against the eROSITA bubbles.

@@

  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time $t=0--1.2$ Myr,\
  allowing the total ejected energy $1.2\times10^{56}$ erg is between\
  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

@@

 \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp} shows\
 the pressure (top), temperature (middile), number density (bottom) of the $x=0$ slices\
 passing through the bipolar jet source injecting along $z=-y$ direction\
 at the end of simulation $t=12.39$ Myr.\
 Comparison between the clumpy (first column from left)\
 and the smooth disc (second) in a stratified atmosphere\
 shows that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (third) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, the two rightmost columns indicate that the development of the innermost bubbles (dashed box)\
 is always associated with the disc, and without the disc,\
 the outermost bubbles and the turbulent region will be tilted,
 indicating the dense disc is crucial for\
 the axis-symmetry of bubbles and for the innermost bubbles formation.

\label{Results}
  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (first column from left)\
             and the smooth disc (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
             Also, the two rightmost columns indicate that the development of the innermost bubbles (dashed box)\
             is always associated with the disc, and without the disc,\
             the outermost bubbles and the turbulent region will be tilted,
             indicating the dense disc is crucial for\
             the axis-symmetry of bubbles and for the innermost bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

  \subsection{X-ray}
  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is calculated\
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\

@@

  Indeed, we find that the simulated gamma-ray\
  spectra for all latitudes exhibit a spectral cutoff at\
  similar energies 400--500 GeV, consistent with\
  the observed cutoff energy.
